Arc Blanc: a real time ocean simulation framework

### 2025-01-29 paper.tex
Precise that we are using single precision float number

Two experiments with different solids have been conducted to demonstrate the efficiency of \framework.
These experiments ran on a \href{https://www.intel.fr/content/www/fr/fr/products/sku/199316/intel-core-i710700-processor-16m-cache-up-to-4-80-ghz/specifications.html}{Intel Core i7-10700} and a \href{https://www.nvidia.com/fr-fr/geforce/graphics-cards/compare/?section=compare-20}{Nvidia GeForce RTX 2070 Super}.
The ocean was simulated with three cascades using a resolution of $256\times265$.
Moreover, the resolution of FDM grids is set to $512\times 512$.

>>>>

Two experiments with different solids have been conducted to demonstrate the efficiency of \framework.
These experiments ran on a \href{https://www.intel.fr/content/www/fr/fr/products/sku/199316/intel-core-i710700-processor-16m-cache-up-to-4-80-ghz/specifications.html}{Intel Core i7-10700} and a \href{https://www.nvidia.com/fr-fr/geforce/graphics-cards/compare/?section=compare-20}{Nvidia GeForce RTX 2070 Super} using single-precision floating-point numbers.
The ocean was simulated with three cascades using a resolution of $256\times265$.
Moreover, the resolution of FDM grids is set to $512\times 512$. 
\begin{figure}[htbp]
	\centering
